---
title: "Human Activity Recognition - Barbell Lifts"
author: "DM"
date: "Tuesday, October 21, 2014"
output: html_document
---

Use data from accelerometers on the belt, forearm, arm, and dumbell of 6 participants. 
They were asked to perform barbell lifts correctly and incorrectly in 5 different ways.
Predict which class they fall into. 

```{r}
library(caret)
library(randomForest)
# Read data
training <- read.csv("data/pml-training.csv")
testing <- read.csv("data/pml-testing.csv")
```

Clean up the data 

```{r}
# Remove summary records  
training <- training[(training$new_window == "no"),]

# Remove first 6 columns
training <- training[,7:ncol(training)]

# Remove columns with non zero variance
nsv <- nearZeroVar(training, saveMetrics=FALSE)
training <- training[,-(nsv)]

```

Split into training and validation datasets 

```{r}
# Split training set into 2 parts
inTrain <- createDataPartition(y=training$classe, p=0.75, list=FALSE)
validation <- training[-inTrain,]
training <- training[inTrain,]
```

Fit a random forest model 

```{r}
set.seed(2454)
rfmod <- randomForest(classe~., data=training) 
```

Predict on validation dataset and get Accuracy 

```{r}
predictions <- predict(rfmod, newdata=validation)
confusionMatrix(predictions, validation$classe) 
```

Predict on the testing dataset

```{r}
# Testing data
predictions <- predict(rfmod, newdata=testing)
pml_write_files = function(x){
    n = length(x)
    for(i in 1:n){
        filename = paste0("answers/problem_id_",i,".txt") 
        write.table(x[i],file=filename,quote=FALSE,row.names=FALSE,col.names=FALSE)
    }
}
#pml_write_files(as.character(predictions))
predictions
```

